---
title: "Data Cleaning"
author: "Your name"
date: "July 11, 2017"
output: html_document
---

### A. "Real Property Taxes" Dataset 

Download the "real property taxes" dataset from the website (via OpenBaltimore), 
he data is located here (note you don\'t need to unzip it to read it into R):
http://sisbid.github.io/Module1/data/Real_Property_Taxes.csv.gz

1. Read the Property Tax data into R and call it the variable `tax`
```{r}
library("readr", lib.loc="/Library/Frameworks/R.framework/Versions/3.4/Resources/library")
tax = read_csv("http://sisbid.github.io/Module1/data/Real_Property_Taxes.csv.gz")
```

2. How many addresses pay property taxes? 

```{r}
nrow(tax)
```

3. What is the total city and state tax paid?
```{r}
state_tax = tax$StateTax %>% str_replace(fixed("$"), "") %>% str_replace(",","") %>% as.numeric

city_tax = tax$CityTax %>% str_replace(fixed("$"), "") %>% str_replace(",","") %>% as.numeric

sum(city_tax, na.rm = TRUE)

glimpse(tax)
View(tax)




```


4. Convert the 'lotSize' variable to a numeric square feet variable. Tips:
* Look at the data 
* Assume hyphens represent inches within square foot meassuremnts 
* Assume decimals within acreage measurements
* 1 acre = 43560 square feet
* Look at the data 

