---
title: "subsetting Lab"
author: "Andrew Jaffe"
date: "July 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this lab you can use the interactive console to explore but please record your commands here.  

Remember anything you type here can be "sent" to the console with: Cmd-Enter (OS-X) or Ctrl-Enter (Windows/Linux).

1. Check to see if you have the `mtcars` dataset (which is included in the `datasets` package)

```{r,load_mtcars}
#rename the rownames to the first column and then set rownames(mtcars) <- NULL
```

2. What class is `mtcars`?

```{r,class}
class(mtcars)
data.frame
```

3. How many observations (rows) and variables (columns) are in the `mtcars` dataset?

```{r, rows_cols}
nrow(mtcars)
ncol(mtcars)
```


4. Select the subset of rows that get more than 20 miles per gallon (mpg) of fuel efficiency - how many are there?
```{r, subset_fuelefficiency}
View(mtcars)
mtcars_fueleff <- mtcars[mtcars$mpg > 20,]
#same as the following
mtcars_fueleff <- filter(mtcars, mpg > 20)
nrow(mtcars_fueleff)
```


5. Select the subset of rows that get less than 16 miles per gallon (mpg) of fuel efficiency and have more than 100 horsepower (hp) - how many are there?

```{r, subset_fuelefficiency_horse}
mtcars_fueleff_horse <- filter(mtcars, mpg < 16 & hp > 100)
nrow(mtcars_fueleff_horse)
```

6. Create a subset of the data that only contains the columns:wt, qsec, and hp for only the cars that have 8 cylinder, and assign this object to `carsSub` - what are the dimensions of this dataset?

```{r, subset_cols}
carsub <- filter(mtcars, cyl == 8) %>% select("wt","qsec","hp")
nrow(carsub)
ncol(carsub)
```

7. Convert the column names of `carsSub` to all upper case
```{r, convert}
colnames(carsub) <- colnames(carsub) 
```

8. Re-order the rows of `carsSub` by weight in increasing order

```{r, convert}
arrange(carsSub, WT)
carsSub[order(carsSub$WT),]
```


9. Copy mtcars into a variable called `cars` and rename the `mpg` column in `cars` to `MPG`

cars <- mtcars


10. Subset the columns from mtcars that end in "p" and call the new data frame `pvars`


